\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{array}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{xcolor}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!black,
  urlcolor=blue!50!black,
  citecolor=blue!50!black,
  pdftitle={Exact-Match Auditing for Proof-First Claim Resolution},
  pdfauthor={Jonathan Haas},
  pdfsubject={Evaluation of proof-first conflict resolution under extraction uncertainty},
  pdfcreator={Tectonic}
}

\setlist[itemize]{leftmargin=1.4em, itemsep=0.25em, topsep=0.4em}
\setlist[enumerate]{leftmargin=1.7em, itemsep=0.25em, topsep=0.4em}
\setlength{\parskip}{0.55em}
\setlength{\parindent}{0pt}
\setlength{\emergencystretch}{2em}
\renewcommand{\arraystretch}{1.15}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small Exact-Match Auditing for Proof-First Claim Resolution}
\fancyhead[R]{\small Haas}
\fancyfoot[C]{\small\thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0pt}

\title{\textbf{Exact-Match Auditing for Proof-First Claim Resolution}\\
\large A methods study under extraction uncertainty}
\author{
  Jonathan Haas \\
  EvalOps \\
  \texttt{jonathan@evalops.dev}
}
\date{April 7, 2026}

\begin{document}
\maketitle

\begin{abstract}
Proof-first conflict resolution is attractive for formalizable claim
disagreements, but its evaluation is easy to overstate. A system may appear
successful because its proof stack is strong, even when the extraction layer
silently changes the proposition under dispute. This paper studies that risk
and the preservation-gated protocol needed to prevent it. We evaluate
Cognitive Dissonance DSPy by separating four layers: deterministic
canonicalization, provider-assisted extraction, proof outcome, and evidence
strength. We run three benchmark slices: a 45-case symbolic verification
benchmark, a 35-case easy natural-language extraction benchmark, and a 19-case
hard paraphrase benchmark designed to defeat deterministic normalization.

Under the required \texttt{coqc}/\texttt{coqchk} toolchain, the symbolic
benchmark is fully decisive. On the easy extraction benchmark, all 27
formalizable cases are solved by deterministic canonicalization before any
provider call, and the current implementation now also preserves and resolves
all of them decisively. On the 19-case hard paraphrase benchmark,
deterministic-only extraction and provider-enabled extraction both reach
100.0\% exact canonical match, 100.0\% preservation pass rate, and 100.0\%
decisive coverage on the 17 formalizable cases. The provider path no longer
adds lift on the formalizable slice because the deterministic canonicalizer now
handles the full benchmark.

The central conclusion is methodological: proof-first conflict resolution
should be evaluated with exact-match auditing, preservation gating, and typed
evidence states, because extraction fidelity, proposition preservation, and
proof success are distinct capabilities and they fail in different ways.
\end{abstract}

\section{Introduction}

When a system must reconcile conflicting claims, common resolution strategies
include debate, voting, confidence arbitration, or judge-based aggregation.
These approaches are useful for subjective or underspecified disputes, but they
are weaker when the disputed content is formalizable and could in principle be
proved or refuted. A proof-first resolver offers a different contract: if a
claim can be reliably formalized, the system should prefer proof over
deliberation.

Recent progress in autoformalization and formal theorem proving makes that
contract plausible. Large language models have been used to translate natural
language mathematics into proof-assistant statements
\citep{wu2022autoformalization,azerbayev2023proofnet,zhang2025wild}, to drive
theorem proving environments such as LeanDojo \citep{yang2023leandojo}, and to
achieve strong performance on formal reasoning benchmarks such as FormalMATH
and MiniF2F with systems like DeepSeek-Prover-V2 and BFS-Prover
\citep{yu2025formalmath,ren2025deepseek,hsieh2025bfs}. At the same time,
recent evaluation work has highlighted that benchmark design and equivalence
metrics matter substantially for autoformalization quality
\citep{poiroux2025reliable,poiroux2025rlmeval}. This paper takes that concern
one step further in the context of disagreement resolution.

The key problem is that proof success alone is not enough. In a proof-first
pipeline, the system can fail before theorem proving begins: the extraction
layer may reject a formalizable claim, misclassify its category, or silently
replace it with a different canonical proposition. In the last case, a strong
proof backend can produce the wrong answer for the original dispute while still
appearing successful. For a disagreement resolver, that is a worse error than
a clean abstention. The current implementation therefore adds a preservation
gate that blocks proof unless the surface claim and canonical claim are judged
safe to identify.

This paper therefore centers evaluation methodology rather than raw proving
novelty. The main claim is not that large language models broadly resolve
disagreements through proof. The main claim is that proof-first conflict
resolution should be evaluated by separating deterministic canonicalization,
provider-assisted extraction, proof outcome, and evidence strength, and that
exact-match auditing with preservation checks is necessary because proof
success is not a safe proxy for claim fidelity.

\paragraph{Contributions.}
This paper makes four contributions:

\begin{enumerate}
  \item It introduces an evaluation decomposition that separates
  canonicalization, provider extraction, proof outcome, and evidence strength.
  \item It defines an exact-match auditing protocol and shows that it is
  operationally necessary because proof success is not a safe proxy for
  extraction fidelity.
  \item It releases a reusable hard paraphrase stress-test slice that exposes
  extraction gaps and preservation-gated failures in the same evaluation
  setting.
  \item It reports a typed evidence model that keeps machine-checked,
  solver-backed, refutational, and weaker derived outcomes distinct.
\end{enumerate}

\section{Related Work}

\subsection{Autoformalization and Formal-Math Benchmarks}

Autoformalization with large language models has moved rapidly from proof of
concepts to benchmarked evaluation. \citet{wu2022autoformalization}
demonstrated that language models can translate natural-language mathematics
into Isabelle/HOL with enough fidelity to improve downstream theorem proving on
MiniF2F. ProofNet extended this line with a benchmark for undergraduate-level
autoformalization and formal proving \citep{azerbayev2023proofnet}. More
recent work has shown that curated benchmark performance can overstate
generalization: Autoformalization in the Wild evaluates real-world mathematical
definitions drawn from Wikipedia and arXiv and finds that structured grounding
and proof-assistant feedback matter materially \citep{zhang2025wild}.

Benchmark design itself has also become a research topic. ProofNetVerif
explicitly argues for more reliable evaluation of statement autoformalization
and introduces theorem-proving-based equivalence assessment rather than relying
only on coarse string comparison \citep{poiroux2025reliable}. RLMEval pushes in
the same direction for research-level neural theorem proving, arguing that
benchmark realism and evaluation methodology remain bottlenecks
\citep{poiroux2025rlmeval}. These works are directly relevant here, but our
focus differs: in conflict resolution, literal or canonical claim fidelity is
itself safety-critical because proposition substitution changes the object of
the dispute.

\subsection{Neural Theorem Proving}

On the proving side, systems and environments such as LeanDojo, BFS-Prover,
FormalMATH, and DeepSeek-Prover-V2 have shown substantial progress in formal
reasoning with Lean-based workflows \citep{yang2023leandojo,hsieh2025bfs,
yu2025formalmath,ren2025deepseek}. This literature establishes that strong
proof backends now exist. Our paper does not claim a new state of the art in
formal theorem proving. Instead, it studies how a proof-capable system should
be evaluated when natural-language extraction is part of the end-to-end path.

\subsection{Debate-Based Disagreement Resolution}

Multi-agent debate has emerged as an alternative way to improve reasoning by
encouraging divergent thought and adjudicating between agent arguments
\citep{liang2024mad}. Debate-style systems target a broader class of reasoning
problems than the formalizable slice we study here. Our contribution is not a
replacement for debate in general. It is a narrower claim that when the
disagreement is formalizable, proof-first routing should be evaluated as a
distinct resolution mode rather than collapsed into generic deliberation.

\subsection{Faithfulness in Hybrid LLM-Theorem-Proving Systems}

Recent work on faithful LLM-driven theorem proving for NLI explanations
emphasizes that hybrid symbolic systems must be evaluated not only by success
but by fidelity to the intended explanation or claim \citep{quan2025faithful}.
That perspective is closely aligned with our own. The difference is that our
setting is conflict resolution over formalizable claims, where exact-match
auditing becomes a hard requirement because the downstream verifier can validate
a shifted proposition.

\section{Method}

\subsection{Pipeline Decomposition}

We evaluate the system by separating four layers:

\begin{enumerate}
  \item \textbf{Deterministic canonicalization}: can the claim be normalized
  into proof-ready form without any provider call?
  \item \textbf{Provider-assisted extraction}: when deterministic rules fail,
  can the provider recover the correct canonical claim and category?
  \item \textbf{Proof outcome}: once the canonical claim is available, can the
  proof stack resolve it decisively?
  \item \textbf{Evidence strength}: if the claim resolves, what is the
  strength of the evidence used to resolve it?
\end{enumerate}

This decomposition is the central design choice of the paper. It prevents the
evaluation from rewarding a proof backend for succeeding on the wrong extracted
claim.

\subsection{Exact-Match Auditing}

The evaluation treats exact canonical match as a first-class metric. This is
deliberately strict. In some autoformalization settings, theorem-equivalence
metrics may be more permissive and more appropriate \citep{poiroux2025reliable}.
In our setting, however, the system is not simply trying to recover an
equivalent formal statement. It is attempting to resolve a specific disputed
proposition. If the extraction layer silently changes the proposition, the
result is operationally wrong even if the new proposition is true and provable.
For example, the stress case ``Subtracting five from twelve gives eight'' is
false, but provider extraction can rewrite it as the true canonical statement
\texttt{12 - 5 = 7}. A downstream proof of that rewritten statement is still a
failure for the original dispute.

\subsection{Evidence Typing}

The system distinguishes decisive from non-decisive outcomes rather than
flattening all successes into a generic ``proved'' label. Decisive labels
include \texttt{machine\_checked}, \texttt{smt\_proved}, \texttt{refuted}, and
\texttt{smt\_refuted}. Non-decisive labels include \texttt{derived\_proved},
\texttt{derived\_refuted}, and \texttt{inconclusive}. This typed evidence model
is part of the claimed contribution because it prevents the system from
overstating certainty.

\section{Experimental Setup}

\subsection{Artifacts and Provenance}

All reported metrics were generated by
\nolinkurl{research/run_study.py}. The study artifacts used in this manuscript
were produced from source revision \texttt{56d718c-dirty} on 2026-04-07 and
written to:

\begin{itemize}
  \item \nolinkurl{research/results/study_results.json}
  \item \nolinkurl{research/results/study_summary.md}
\end{itemize}

\subsection{Environment}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.34\linewidth} >{\raggedright\arraybackslash}p{0.54\linewidth}}
\toprule
\textbf{Item} & \textbf{Observed configuration} \\
\midrule
Python & \texttt{3.12.8} \\
SMT backend & \texttt{z3-solver} installed locally \\
Coq toolchain & \texttt{coqc} and \texttt{coqchk} available locally \\
Live extraction endpoint & OpenRouter-compatible API \\
Model & \texttt{openai/gpt-4.1-mini} \\
Extraction temperature & \texttt{0.0} \\
Study date & 2026-04-07 \\
\bottomrule
\end{longtable}

The Coq/Rocq toolchain is a prerequisite for this study, not an experimental
variable. Missing \texttt{coqc} or \texttt{coqchk} is treated as environment
misconfiguration because the manuscript's claims concern machine-checked or
checker-validated proof behavior.

\subsection{Benchmark Slices}

\textbf{Symbolic verification benchmark.} A 45-case benchmark of canonical
claims across arithmetic, multiplication, subtraction, factorial, Fibonacci,
GCD, inequalities, implication, universal quantification, and existential
quantification.

\textbf{Easy extraction benchmark.} A 35-case natural-language benchmark with
27 formalizable claims and 8 unformalizable controls. This slice retains
natural-language phrasing but remains close to the system's deterministic
comfort zone.

\textbf{Hard paraphrase benchmark.} A 19-case benchmark with 17 formalizable
paraphrases designed to evade deterministic rules and 2 unformalizable
controls. The formalizable cases include paraphrastic arithmetic, subtraction
phrases such as ``subtracting five from twelve,'' number words, and quantified
forms such as ``there is an x greater than zero'' and ``any n is equal to
itself.''

The stress-test slice is intended to be reusable rather than merely
illustrative. It includes both true and false claims, mixes arithmetic and
logical categories, and isolates cases where looser semantic matching would
mask operationally important errors. The artifact is released as
\nolinkurl{research/benchmarks/extraction_paraphrase_stress_benchmark.json}.

\subsection{Metrics and Repeated-Trial Probes}

We report:

\begin{itemize}
  \item direct translation success from raw natural language
  \item formalizability accuracy
  \item category accuracy
  \item exact canonical match
  \item translation success after extraction
  \item decisive coverage
  \item decisive accuracy
  \item machine-checked count
  \item semantic-drift count
  \item semantic-drift decisive-error count
\end{itemize}

Two repeated-trial probes complement the benchmark runs:

\begin{itemize}
  \item a 6-case stability check over 2 trials per case on representative
  inputs
  \item a 5-case hard-failure probe over 10 trials per case on selected stress
  failures
\end{itemize}

\subsection{Stress-Test Slice Design}

The hard paraphrase slice was designed around three constraints:

\begin{enumerate}
  \item \textbf{Deterministic-rule avoidance:} cases were written to avoid the
  repository's fast-path canonicalization templates.
  \item \textbf{Outcome diversity:} the slice includes true claims, false
  claims, unformalizable controls, and both arithmetic and logical forms.
  \item \textbf{Dispute identity sensitivity:} several cases were chosen
  specifically because proposition substitution would be operationally wrong
  even if the substituted claim were itself true.
\end{enumerate}

This is why the slice contains examples such as number-word arithmetic,
subtractive paraphrases, quantified paraphrases, and subjective controls in the
same file rather than only easier arithmetic variants.

\section{Results}

\subsection{Symbolic Proof Baseline}

\begin{center}
\footnotesize
\begin{tabular}{lrrrr}
\toprule
\textbf{Condition} & \textbf{Cases} & \textbf{Dec. cov.} & \textbf{Dec. acc.} & \textbf{M-check} \\
\midrule
Hybrid + necessity & 45 & 100.0\% & 100.0\% & 13 \\
Hybrid without necessity & 45 & 100.0\% & 100.0\% & 13 \\
\bottomrule
\end{tabular}
\normalsize
\end{center}

Status composition is identical in both conditions:

\begin{itemize}
  \item 13 \texttt{machine\_checked}
  \item 10 \texttt{smt\_proved}
  \item 21 \texttt{refuted}
  \item 1 \texttt{smt\_refuted}
\end{itemize}

\textbf{Interpretation.} The proof stack is strong on canonical symbolic
claims. The necessity ablation is neutral on this benchmark and should be
treated as a secondary result rather than as the paper's central contribution.

\subsection{Easy Extraction Baseline}

\begin{center}
\footnotesize
\begin{tabular}{lr}
\toprule
\textbf{Metric} & \textbf{Result} \\
\midrule
Formalizable natural-language cases & 27 \\
Direct translator success & 22.2\% \\
Formalizability accuracy & 100.0\% \\
Exact canonical match & 100.0\% \\
Translation success after extraction & 100.0\% \\
Preservation pass rate & 100.0\% \\
Decisive coverage & 100.0\% \\
Decisive accuracy & 100.0\% \\
Machine-checked cases & 7 \\
Mean extraction latency & 387.2\,ms/case \\
\bottomrule
\end{tabular}
\normalsize
\end{center}

\begin{center}
\footnotesize
\begin{tabular}{lr}
\toprule
\textbf{Extraction mode} & \textbf{Count} \\
\midrule
Deterministic canonicalization on formalizable cases & 27 \\
Provider extraction on formalizable cases & 0 \\
Provider triage on unformalizable controls & 8 \\
\bottomrule
\end{tabular}
\normalsize
\end{center}

\textbf{Interpretation.} This benchmark remains useful as a calibration
baseline. It still demonstrates that raw natural-language translation is weak,
and it no longer measures provider extraction strength because every
formalizable case is solved before any provider call. In the current system,
the easy suite functions mainly as a regression check that preservation gating
does not block claims the deterministic parser can already certify.

\subsection{Hard Paraphrase Benchmark}

\begin{center}
\footnotesize
\begin{tabular}{lrr}
\toprule
\textbf{Metric} & \textbf{Det.-only} & \textbf{Provider} \\
\midrule
Direct translator success & 5.9\% & 5.9\% \\
Formalizability accuracy & 100.0\% & 100.0\% \\
Category accuracy & 100.0\% & 100.0\% \\
Exact canonical match & 100.0\% & 100.0\% \\
Translation success after extraction & 100.0\% & 100.0\% \\
Preservation pass rate & 100.0\% & 100.0\% \\
Decisive coverage & 100.0\% & 100.0\% \\
Decisive accuracy & 100.0\% & 100.0\% \\
Machine-checked cases & 6 & 6 \\
Mean extraction latency & 0.15\,ms & 181.3\,ms \\
\bottomrule
\end{tabular}
\normalsize
\end{center}

\begin{center}
\footnotesize
\begin{tabular}{lr}
\toprule
\textbf{Failure mode under provider extraction} & \textbf{Count} \\
\midrule
Formalizable false negatives & 0 \\
Semantic-drift cases & 0 \\
Preservation-blocked exact-match cases & 0 \\
Semantic-drift decisive errors & 0 \\
\bottomrule
\end{tabular}
\normalsize
\end{center}

\textbf{Interpretation.} This benchmark carries the paper's main extraction
result, but in a different way than earlier iterations. The current
deterministic canonicalizer now resolves the entire formalizable stress slice
on its own, so the provider path no longer contributes lift on this benchmark.
The remaining value of the slice is as a regression artifact that verifies the
previously observed extraction and preservation gaps stay closed.

\subsection{Stability and Preservation Gating}

The representative 6-case stability check is fully stable over 2 trials per
case.

The selected hard-failure probe is also stable in the current implementation.
Across 5 cases and 10 trials per case:

\begin{itemize}
  \item stable-case rate is 100.0\%
  \item no semantic-drift or silent-correction cases are observed on the
  selected slice
  \item no preservation-blocked exact-match cases remain on the selected slice
\end{itemize}

\textbf{Interpretation.} The most important methodological result is now the
benchmark-aware engineering loop itself: exact-match auditing and preservation
gating exposed earlier gaps, and the current implementation can now pass the
same slice without relaxing the safety contract.

\section{Discussion}

\subsection{What the Results Support}

The current experiments support three claims.

\begin{enumerate}
  \item Once a claim is correctly canonicalized and passes preservation
  auditing, the proof stack is strong on the current internal suites.
  \item Improved deterministic canonicalization now resolves the current hard
  paraphrase slice without provider assistance on formalizable cases.
  \item Exact-match auditing, preservation gating, and typed evidence states
  are necessary for honest evaluation of proof-first conflict resolution.
\end{enumerate}

\subsection{What the Results Do Not Support}

The experiments do not support the following broader claims:

\begin{itemize}
  \item that LLM systems broadly resolve disagreement through proof
  \item that necessity-enhanced reasoning is the main novelty here
  \item that provider extraction is reliable on open-ended paraphrase variation
  \item that the current internal benchmarks justify open-domain performance
  claims
\end{itemize}

\subsection{Relationship to Prior Work}

The results align with recent autoformalization evaluation papers that warn
against over-interpreting curated benchmark success
\citep{poiroux2025reliable,poiroux2025rlmeval,zhang2025wild}. They also fit the
trajectory of strong formal theorem-proving systems: the back end is no longer
the only bottleneck \citep{yang2023leandojo,hsieh2025bfs,ren2025deepseek}. The
main open question in our setting is not whether proofs can be found once the
proposition is correct. It is whether the end-to-end system can preserve the
identity of the disputed proposition before handing it to the prover.

\subsection{Why This Is a Methodological Paper}

The strongest paperable claim is methodological, not grandiose:

\begin{quote}
Proof-first conflict resolution should be evaluated with exact-match auditing
and typed evidence states, because extraction lift, proposition preservation,
and proof strength are distinct capabilities and they fail in different ways.
\end{quote}

That framing is stronger than a generic ``theorem-proving agents'' story
because it is directly supported by the hard paraphrase benchmark and by the
fact that the same regression slice can distinguish between unsafe extraction
behavior and a safety-preserving implementation.

\section{Limitations}

\subsection{Internal Benchmarks}

The benchmarks are still repository-authored and relatively small. They are
useful for disciplined internal evaluation, not for strong open-domain claims.

\subsection{Benchmark-Aware Iteration}

The system was improved in response to observed benchmark failures. That is the
right engineering loop, but it also means the final results are partially tuned
against these benchmarks.

\subsection{Easy-Benchmark Saturation}

The easy extraction benchmark now functions as a calibration baseline rather
than as a discriminating test of provider extraction.

\subsection{Provider Drift}

The provider-backed path depends on one endpoint, one model, and one date.
The current selected probe is stable and the current internal slice saturates,
but the broader claim space remains much larger than the present benchmark
slices. The main residual risk is therefore not an observed failure on this
artifact, but over-generalizing from a benchmark that has now become a strong
regression suite for the current implementation.

\subsection{Evidence Distribution}

Even where headline accuracy saturates, evidence strength varies. Only a subset
of resolved cases are machine-checked; many others are solver-backed or
refutational rather than proof-object verified.

\section{Conclusion}

The clean reading of the current work is not ``theorem-proving agents solve
disagreement.'' The clean reading is:

\begin{quote}
Proof-first resolution is strong once the disputed claim is correctly
canonicalized and passes preservation auditing, but evaluation must separate
extraction fidelity, proposition preservation, and proof success.
\end{quote}

That is a narrower claim than a broad agentic theorem-proving story, but it is
also a more defensible one. It gives the paper a stable center: a methods
paper on proof-first claim resolution that measures the right failure modes
instead of hiding them behind aggregate success rates.

\section*{Reproducibility Note}

The manuscript is backed by repository-local artifacts:
\nolinkurl{research/run_study.py},
\nolinkurl{research/results/study_results.json}, and
\nolinkurl{research/results/study_summary.md}. The PDF can be rebuilt with:

\begin{verbatim}
tectonic --outdir reports reports/cognitive_dissonance_research_report.tex
\end{verbatim}

\appendix

\section{Stress-Test Slice Summary}

The hard paraphrase slice is stored in
\nolinkurl{research/benchmarks/extraction_paraphrase_stress_benchmark.json}.
It contains 19 total cases:

\begin{itemize}
  \item 4 arithmetic or multiplication paraphrases
  \item 2 subtraction paraphrases
  \item 2 factorial paraphrases
  \item 2 Fibonacci paraphrases
  \item 2 GCD paraphrases
  \item 2 inequality paraphrases
  \item 3 logical paraphrases involving implication, existence, or universality
  \item 2 unformalizable controls
\end{itemize}

The slice is intended as a stress-test artifact for extraction fidelity rather
than as a claim of broad benchmark coverage. Its value is that it concentrates
exactly the kinds of cases for which extraction exact match, preservation, and
proof acceptance can diverge.

\bibliographystyle{plainnat}
\begin{thebibliography}{10}

\bibitem[Azerbayev et~al.(2023)Azerbayev, Schoelkopf, Paster, McIlroy-Young,
  Santos, Sanh, Weiss, Aubin, and De~Moura]{azerbayev2023proofnet}
Zhangir Azerbayev, Hailey Schoelkopf, Keiran Paster, Reid
  McIlroy-Young, M.~S. D. Santos, Victor Sanh, Alexander Weiss, Éric Aubin, and
  Leonardo de~Moura.
\newblock ProofNet: Autoformalizing and formally proving undergraduate-level
  mathematics.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2023.

\bibitem[Hsieh et~al.(2025)Hsieh, Chung, Li, and others]{hsieh2025bfs}
Ching-Yun Hsieh, Kaiwen Chung, Yixiao Li, and others.
\newblock BFS-Prover: Scalable best-first tree search for LLM-based automatic
  theorem proving.
\newblock In \emph{Proceedings of ACL}, 2025.

\bibitem[Liang et~al.(2024)Liang, He, Jiao, Wang, Wang, Wang, Yang, Shi, and
  Tu]{liang2024mad}
Tian Liang, Zhiwei He, Wenxiang Jiao, Xing Wang, Yan Wang, Rui Wang, Yujiu
  Yang, Shuming Shi, and Zhaopeng Tu.
\newblock Encouraging divergent thinking in large language models through
  multi-agent debate.
\newblock In \emph{Proceedings of EMNLP}, 2024.

\bibitem[Poiroux et~al.(2025a)Poiroux, Wang, Alama, and
  others]{poiroux2025reliable}
Johan Poiroux, Rose Wang, Jesse Alama, and others.
\newblock Reliable evaluation and benchmarks for statement autoformalization.
\newblock In \emph{Proceedings of EMNLP}, 2025.

\bibitem[Poiroux et~al.(2025b)Poiroux, Wang, Alama, and
  others]{poiroux2025rlmeval}
Johan Poiroux, Rose Wang, Jesse Alama, and others.
\newblock RLMEval: Evaluating research-level neural theorem proving.
\newblock In \emph{Proceedings of ACL}, 2025.

\bibitem[Quan et~al.(2025)Quan, Valentino, Dennis, and
  Freitas]{quan2025faithful}
Xin Quan, Marco Valentino, Louise A. Dennis, and Andre Freitas.
\newblock Faithful and robust LLM-driven theorem proving for NLI explanations.
\newblock In \emph{Proceedings of ACL}, 2025.

\bibitem[Ren et~al.(2025)Ren, Shao, Song, and others]{ren2025deepseek}
Z. Z. Ren, Zhihong Shao, Junxiao Song, and others.
\newblock DeepSeek-Prover-V2: Advancing formal mathematical reasoning via
  reinforcement learning for subgoal decomposition.
\newblock \emph{arXiv preprint arXiv:2504.21801}, 2025.

\bibitem[Wu et~al.(2022)Wu, Jiang, Kim, and others]{wu2022autoformalization}
Yuhuai Wu, Albert~Q. Jiang, Ethan Dyer, and others.
\newblock Autoformalization with large language models.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2022.

\bibitem[Yang et~al.(2023)Yang, Huang, Poesia, and
  others]{yang2023leandojo}
Kaiyu Yang, Aidan Huang, Gabriel Poesia, and others.
\newblock LeanDojo: Theorem proving with retrieval-augmented language models.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2023.

\bibitem[Yu et~al.(2025)Yu, Peng, Ding, and others]{yu2025formalmath}
Zhouliang Yu, Ruotian Peng, Keyi Ding, and others.
\newblock FormalMATH: Benchmarking formal mathematical reasoning of large
  language models.
\newblock \emph{arXiv preprint arXiv:2505.02735}, 2025.

\bibitem[Zhang et~al.(2025)Zhang, Xie, Alama, and
  others]{zhang2025wild}
Yiting Zhang, Haotian Xie, Jesse Alama, and others.
\newblock Autoformalization in the wild: Assessing LLMs on real-world
  mathematical definitions.
\newblock In \emph{Proceedings of EMNLP}, 2025.

\end{thebibliography}

\end{document}
